---
title: "Eatontown Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(tidyverse)
library(plotly)
library(DT)

knitr::opts_chunk$set (echo=FALSE, message=FALSE)

# Yikes looks like https://datausa.io/profile/geo/eatontown-nj already does this
```

Demographics
=====================================  
    
Row {data-height=250}
-------------------------------------
    
### Total Population
    
```{r}
pop_total <- data.frame(year=c("2010","2011","2012","2013","2014","2015","2016","2017","2018","2019","2020"),
                estimate=c(12459,12320,12249,12206,12181,12198,12238,12297,12238,12175,12132))

plot_pop_total <- ggplot(pop_total, aes(x=year, y=estimate, group=1)) +
  geom_line()+
  geom_point()

ggplotly(plot_pop_total)
```

> vastly different estimates between https://data.census.gov/cedsci/table?q=eatontown and https://nj.gov/labor/lpa/dmograph/est/mcdest2009.htm

Row {data-height=250}
-------------------------------------
   
### Population by Race

```{r}
pop_race <- read_csv("data/population_by_race.csv")

plot_pop_race <- ggplot(pop_race, aes(fill=Race, y=Estimate, x=Year)) + 
    geom_bar(position="stack", stat="identity") + 
    scale_fill_manual(values = c("gray", "snow4", "gray39"))

ggplotly(plot_pop_race)

```   

> Mocked up for now. OPRA request or Census data?

### Population by Age Group
    
```{r}
pop_age <- read_csv("data/population_by_age.csv")

plot_pop_age <- ggplot(pop_age, aes(fill=Group, y=Estimate, x=Year)) + 
    geom_bar(position="stack", stat="identity") + 
    scale_fill_manual(values = c("gray", "snow4", "gray39"))

ggplotly(plot_pop_age)
```

> Mocked up for now. OPRA request or Census data?

Row {data-height=250}
-------------------------------------
   
### Median Household Income

```{r}
household_income <- data.frame(year=c("2010","2011","2012","2013","2014","2015","2016","2017","2018","2019","2020"),
                estimate=c(58012,58821,59921,60013,58101,61358,63293,63555,63201,66001,66125))

plot_household_income <- ggplot(household_income, aes(x=year, y=estimate, group=1)) +
  geom_line()+
  geom_point()

ggplotly(plot_household_income)
```   

> Mocked up for now. OPRA request or Census data?

### Median Household Income Brackets [grouped bar]
    
```{r}
income_age <- read_csv("data/income_by_age.csv")

plot_income_age <- ggplot(income_age, aes(fill=Group, y=Estimate, x=Year)) + 
    geom_bar(position="dodge", stat="identity") + 
    scale_fill_manual(values = c("gray", "snow4", "gray39"))

ggplotly(plot_income_age)
```

> OPRA request or Census data?

Financials
=====================================     
   
Row {data-height=250}
-------------------------------------

### Budget

```{r}
budget <- data.frame(year=c("2010","2011","2012","2013","2014","2015","2016","2017","2018","2019","2020"),
                amount=c(21.0,22.0,22.6,23.05,23.35,23.9,24.9,25.0,26.25,27.7,28.66))

plot_budget <- ggplot(budget, aes(x=year, y=amount, group=1)) +
  geom_line()+
  geom_point() +
  ylab("amount in millions")

ggplotly(plot_budget)
```

> OPRA request: "Yearly starting budget from 2010 to 2020."?

Row {data-height=250}
-------------------------------------
   
### Deficit/Surplus [time-series]

```{r}
```   

> OPRA Request: "Yearly ending deficit/surplus from 2010 to 2020."?

### Expenditures by Category [horizontal grouped bar]

```{r}
expenditures <- read_csv("data/expenditures.csv")

plot_expenditures <- ggplot(expenditures, aes(fill=Category, y=Amount, x=Year)) + 
    geom_bar(position="stack", stat="identity") + 
    scale_fill_manual(values = c("gray", "snow4", "gray39", "gray20", "gray10"))

ggplotly(plot_expenditures)
```

> OPRA request: "Yearly spend by category from 2010 to 2020."?

Row {data-height=250}
-------------------------------------
   
### Salary by Department

```{r}
salary <- read_csv("data/salary.csv")

plot_salary <- ggplot(salary, aes(fill=Category, y=Amount, x=Year)) + 
    geom_bar(position="stack", stat="identity") + 
    scale_fill_manual(values = c("gray", "snow4", "gray39", "gray20", "gray10")) + 
    coord_flip()

ggplotly(plot_salary)
```   

> OPRA request: "Total paid compenstation for all employees from 2010 to 2020. Include year, name, department, and total compenstation including overtime."?

Row
-------------------------------------

### Top Compensation Earners

```{r}
df <- data.frame(Name=rep(c('A', 'B', 'C', 'D'), each=4),
                 Department=rep(c('G', 'F'), times=8),
                 Compensation=round(runif(16, 4, 20),0))

datatable(df, rownames=FALSE, height=500)
```

> Re-use data from "Salary by Department" request.

Land Use
=====================================

Row {data-height=250}
-------------------------------------

### Median Household Price [time-series]

```{r}

```   

> OPRA request or Census data?

Row {data-height=250}
-------------------------------------

### Dwelling Types [by type (apt, house, etc.), time-series]

```{r}

```   

> OPRA request or Census data?

### Housing Types [by type (rent, own, etc.), time-series]

```{r}
```

> OPRA request or Census data?

Row {data-height=250}
-------------------------------------

### Development Permits Granted [by type, time-series]

```{r}
```   

> OPRA Request: "Permits granted from 2010 to 2020. Include date, permit type, requestor, grantor."

Row {data-height=250}
-------------------------------------

### Top Permit Requestors [datatable]

```{r}
```

> Re-use data from "Development Permits Granted" request.

### Top Variance Requestors [datatable]

```{r}
```

> OPRA Request: "Variances granted from 2010 to 2020. Include date, permit type, requestor, grantor."


