---
title: "Eatontown Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(lubridate)
library(ggplot2)
library(tidyverse)
```

Demographics
=====================================  
    
Row
-------------------------------------
    
### Total Population [time-series]
    
```{r}
```

> OPRA request or Census data?

Row
-------------------------------------
   
### Population by Race [time-series]

```{r}
```   

> OPRA request or Census data?

### Population by Age Group [grouped bar]
    
```{r}
```

> OPRA request or Census data?

Row
-------------------------------------
   
### Median Household Income [time-series]

```{r}
```   

> OPRA request or Census data?

### Median Household Income Brackets [grouped bar]
    
```{r}
```

> OPRA request or Census data?

Financials
=====================================     
   
Row
-------------------------------------

### Budget [time-series]

```{r}
```

> OPRA request: "Yearly starting budget from 2010 to 2020."?

Row
-------------------------------------
   
### Deficit/Surplus [time-series]

```{r}
```   

> OPRA Request: "Yearly ending deficit/surplus from 2010 to 2020."?

### Spend by Category [grouped bar]

```{r}
```

> OPRA request: "Yearly spend by category from 2010 to 2020."?

Row
-------------------------------------
   
### Salary by Department [time-series]

```{r}
```   

> OPRA request: "Total paid compenstation for all employees from 2010 to 2020. Include year, name, department, and total compenstation including overtime."?

### Top Salary Earners [datatable]

```{r}
```

> Re-use data from "Salary by Department" request.

Land Use
=====================================     
   
Row
-------------------------------------

### Zones [by type (res, comm, indust, agri), time-series]

```{r}
```  

> OPRA request or Census data?

Row
-------------------------------------

### Median Household Price [time-series]

```{r}
```   

> OPRA request or Census data?

Row
-------------------------------------

### Dwelling Types [by type (apt, house, etc.), time-series]

```{r}
```   

> OPRA request or Census data?

### Housing Types [by type (rent, own, etc.), time-series]

```{r}
```

> OPRA request or Census data?

Row
-------------------------------------

### Development Permits Granted [by type, time-series]

```{r}
```   

> OPRA Request: "Permits granted from 2010 to 2020. Include date, permit type, requestor, grantor."

Row
-------------------------------------

### Top Permit Requestors [datatable]

```{r}
```

> Re-use data from "Development Permits Granted" request.

### Top Variance Requestors [datatable]

```{r}
```

> OPRA Request: "Variances granted from 2010 to 2020. Include date, permit type, requestor, grantor."


